\chapter{Other Considerations}

\section{Late Additions}
Since the first day of this project we knew we would eventually be handling some SCADA protocol(s). Throughout development our client was often unsure what protocols were necessary, but told us they would let us know as soon as they could. In mid-March, we finally received word that we needed to be using the DNP3 protocol. This was initially somewhat alarming as we had no previous knowledge of the protocol, and we only had a month and a half to learn about it and implement it. There were also some issues regarding specifics of the protocol as we needed to make sure we were exactly matching our client's. Luckily, with the aforementioned plugin framework, we were able to rapidly implement the requested functionality after learning the necessary pieces of the protocol. Adding significant functionality so late in the development process can be rather detrimental to a project, however we were able to complete the work requested and it is currently implemented.


The other late addition was not a technical one. Halfway through the project, we were given an additional team member. This initially seemed really beneficial as we had plenty of work that needed to get done. Luckily, Brooks' Law did not hold in our circumstance. There was plenty of trying to get our new member up to speed on not only what our project was about, but also the technical details of it. This addition was surely unexpected, but it definitely gave our team an idea of potential outcomes given personnel changes during a project.
