\section{Project Description}

\subsection{Background}
\begin{frame}
\frametitle{Background}

\todo[inline]{Very first slide shouldn't be background. It should
be something concise that describes our overall project in very highlevel
terms, "Our project is blah blah blah" with a picture or something so you
can just talk about it for a minute. Background slide should come second.}
\begin{block}{The Problem}
SCADA networks around the country face the threat of intrusions everyday. Keeping these networks secure and safe is of utmost importance.
\end{block}
\todo[inline]{Drop the corporate-speak "of utmost importance." Just say
something about industrial networks seeing frequent attacks and being a
high-value target.}

Supervisory Control And Data Acquisition (SCADA) networks are highly automated industrial control systems which are utilized in:
\begin{itemize} % Elaborate on each item
\item Power plants
\item Water treatment facilities
\item Civil defense systems
\item Commercial transportation systems
\end{itemize}

\todo[inline]{Take this sentence "Because of the importance..." off the slide.
It's fine to say it out loud when you give your presentation, but no reason
to actually put it on the slide.}
    Because of the importance of these networks it is crucial that they be kept secure from any and all attacks.
\end{frame}



\begin{frame}
\frametitle{Background Cont.}
%\column{.65\textwidth} % Left column and width

\todo[inline]{Don't use "Continued" slides. We don't have that much content.}
\todo[inline]{This "Why the threat" part should not be on this slide. You
should just say this part out loud.}
\todo[inline]{The "Goal" and "Criteria for Success" belong on their own slide.
You should make this slide about that instead of "Background Cont."}

\begin{itemize}
\item \textbf{Why the threat? } \begin{itemize}\item SCADA networks are often located in facilities which may be hard to reach
\item High life expectancy.
\item Down-Time limitations = difficult to update.
\end{itemize} 
\item \textbf{Goal: }To create a small standalone device for 28 of Alliant Energy's Supervisory Control  And Data Acquisition networks.
\item \textbf{Criteria For Success: }A small standalone device capable of replicating false  SCADA protocols to fool potential attacker.  The device should also be able to log  attack parameters and alert administrative personnel for action.
\end{itemize}

%\column{.2\textwidth} % Right column and width
%\end{columns}

\end{frame}

\subsection{Project Requirements}
\begin{frame}
\frametitle{Project Requirements}

\todo[inline]{bullet 1: ok, bullet 2: ok, bullet 3: typo "basic other basic". also, don't say "other" here because SSH/HTTP/S are not SCADA. also, mention these are *honeypots*, not the actual protocol. bullet 4: don't say "Small passive", say "Minimal", bullet 5: i don't like how you've phrased this...it sounds weird. bullet 6: Again, weird phrasing and doesn't flow with other points.}

% TODO: write your slide here
\begin{itemize}
\item Small, low interaction device
\item Durable and low maintenance
\item Support of SSH, HTTP/S and basic other basic SCADA protocols
\item Small passive intrusion detection system
\item Capable of capturing attacker data and credentials
\item Ability to log attacks and forward them to administrative personnel
\end{itemize}

\end{frame}

